---
title: "ev_summaries.Rmd"
author: "W. Probert"
date: "29/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
require(ggplot2)
require(tidyverse)
require(reshape2)
library(gt)
```


## Projections

#### Visual summary of the projections

```{r}
# Parameters
ev_datasets <- c(
    "ebola_data_cleaned.csv")

# Read the data
dataset_list <- list(); i <- 1
for(dataset in ev_datasets){
  df <- read.csv(file.path("..", "..", "data", "processed", dataset))
  df_long <- melt(df, id.vars = c("model"))
  df_long$dataset <- dataset
  dataset_list[[i]] <- df_long; i <- i + 1
}
df_values <- do.call(rbind, dataset_list)

# Make variables plot nicely
df_values <- rename(df_values, intervention = variable)

df_values$intervention_label <- paste0(toupper(substring(df_values$intervention, 1, 1)),
                                       substring(df_values$intervention, 2))
df_values$intervention_label <- gsub("_", " ", df_values$intervention_label)
df_values$objective <- "Cases"
df_values$run <- 1
```


```{r, fig.width = 10, fig.height = 8}
# Plot projections across models and interventions
ggplot(df_values, aes(y = model, x = value,
                      colour = intervention_label, fill = intervention_label)) +
  geom_point(size = 3.5, alpha = 0.8) + 
  scale_fill_brewer(name = "Intervention", palette = "Set1") +
  scale_colour_brewer(name = "Intervention", palette = "Set1") +
  scale_x_continuous(labels = scales::comma) +
  xlab("Projected caseload") + ylab("Model") +
  theme_classic() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 8),
    axis.title = element_text(size = 16),
    legend.text = element_text(size = 14)
  )
```

$$\\[1in]$$

#### Table of summary statistics of the projections

There is one mean value per model, so refer to raw data.  

$$\\[1in]$$

### Summaries of ties in **within-model** rankings of projections of interventions

Proportion of times that ties occur in the minimum projected value, stratified by objective and model. **No ties occur in EV data**.  

$$\\[0.25in]$$

```{r}
df_ties <- df_values %>%
  group_by(model, objective, run) %>%
  mutate(number_winners = sum(value[!is.na(value)] == min(value[!is.na(value)]))) %>%
  arrange(model, objective, run, number_winners) %>%
  select(model, objective, run, number_winners)

df_ties <- df_ties %>%
  mutate(ties_in_winner = number_winners > 1) %>%
  group_by(model, objective) %>%
  summarise(
    prop_ties = 100*mean(ties_in_winner),
    .groups = 'drop')

as.data.frame(df_ties) %>%
  gt(
    rowname_col = "objective",
    groupname_col = "model") %>%
  tab_header(title = "Percent of runs in which there are ties in **best** intervention across models, objectives") %>%
  fmt_number(
    columns = vars(prop_ties),
    decimals = 1,
    use_seps = FALSE
  )
```

$$\\[1in]$$

### Summaries of votes for each intervention (as used in the analysis)

Given there are no ties in converting the projections to ranks, votes are simply within-model ranks of interventions (rank wrt minimizing caseload).  

$$\\[0.25in]$$

```{r}
# Parameters
ev_datasets <- c(
    "ebola_data_votes_str_cases.csv")

# Read the data
dataset_list <- list(); i <- 1
for(dataset in ev_datasets){
  df <- read.csv(file.path("..", "..", "data", "processed", dataset))
  df$dataset <- dataset
  dataset_list[[i]] <- df; i <- i + 1
}
df_values <- do.call(rbind, dataset_list)
df_values$model <- paste("Model", df_values$model)
```

```{r}
df_values_long <- melt(df_values, id.vars = c("model"))
df_values_long <- df_values_long %>% rename(ranking = variable)
df_values_long <- df_values_long %>% rename(intervention = value)
df_values_long$ranking <- as.numeric(substr(df_values_long$ranking, 5, 5))

df_summ <- df_values_long %>% 
  select(ranking, intervention) %>%
  group_by(ranking, intervention) %>%
  count()

df_summ %>% 
  pivot_wider(names_from = ranking, values_from = n) %>%
  gt()
```


```{r}
df_values$rank1 <- toupper(df_values$rank1)
df_values$rank1 <- factor(df_values$rank1, levels <- toupper(unique(df_long$variable)))

df_votes <- df_values %>%
  count(rank1, .drop = FALSE) %>%
  mutate(percent = 100*n/sum(n))

as.data.frame(df_votes) %>%
  gt() %>%
  tab_header(title = "Percent of simulations in which each intervention is voted as **best** across models",
             subtitle = "") %>%
  fmt_number(
    columns = vars(percent),
    decimals = 0,
    use_seps = FALSE
  )

```

$$\\[1in]$$

```{r}
df_values$rank6 <- toupper(df_values$rank6)
df_values$rank6 <- factor(df_values$rank6, levels <- toupper(unique(df_long$variable)))

df_votes <- df_values %>%
  count(rank6, .drop = FALSE) %>% 
  mutate(percent = 100*n/sum(n))

as.data.frame(df_votes) %>%
  gt() %>%
  tab_header(title = "Percent of simulations in which each intervention is voted as **worst** across models",
             subtitle = "") %>%
  fmt_number(
    columns = vars(percent),
    decimals = 0,
    use_seps = FALSE
  )
```

$$\\[1in]$$
